%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Software Engineer \acvHeaderSocialSep {\fontsize{8pt}{1em}\bodyfont\upshape\color{graytext} TypeScript · PostgreSQL · Redis · Terraform · Kubernetes · AWS}} % Job title
{Xendit} % Organization
{Taipei, Taiwan (Remote)} % Location
{Aug. 2021 --- Current} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Developed a financial backend service in a 10+ engineers agile team using high-collab. approaches like \textbf{remote pair programming}}
    \item {Migrated \& deployed a distributed system to be production ready on AWS EKS with minimal downtime of \textbf{4 minutes}}
    \item {Proposed \textbf{solution architectures}, provisioned infra. \& CI/CD pipelines for 8+ services on \textbf{10+} different AWS services managed by Terraform}
    \item {Served as team lead administrator of AWS; \textbf{conducted investigations} \& resolved 4+ production incidents for multiple teams}
  \end{cvitems}
}

%---------------------------------------------------------
  \cventry
    {Senior Engineer \acvHeaderSocialSep {\fontsize{8pt}{1em}\bodyfont\upshape\color{graytext} TypeScript · Python · GraphQL · Kubernetes · AWS}} % Job title
    {Trend Micro} % Organization
    {Taipei, Taiwan} % Location
    {Sep. 2019 --- Jul. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Integrated internal intelligence API services using \textbf{GraphQL} and \textbf{Kubernetes} for \texttt{\char`\~}400 engineers and threat researchers in threat hunting}
        \item {Moved an on-promise system to AWS. Built containerized scalable deployment with AWS Fargate \& CDK which reduced \texttt{\char`\~}20\% of cost}
        \item {Served as team lead administrator of \textbf{Kubernetes} on AWS; operated 3 clusters \& 10+ production workloads}
        \item {Introduced IaC tool \textbf{AWS CDK} to our team; provisioned 4 system infrastructures that consist of 6+ different AWS services like AWS Glue, Step Functions \& RDS}
        \item {Optimized CI/CD pipelines for 6+ projects using prebuilt images, caching \& parallelism; adopted conventional commits \& semantic versioning that reduced up to \textbf{75\%} of deployment time}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {FullStack Engineer \acvHeaderSocialSep {\fontsize{8pt}{1em}\bodyfont\upshape\color{graytext} Node.js · MongoDB · GCP}} % Job title
    {Ugotit Design Inc.} % Organization
    {Taipei, Taiwan} % Location
    {Feb. 2019 --- Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed \& implemented scalable systems with Google App Engine \& Cloud Scheduler that served \textbf{250+} concurrent users and above \textbf{500 QPS}}
        \item {Served as tech lead \& system architect of 4 web-based game projects that generated revenue of over \textbf{1 million} for the company in 7 months}
        \item {Focused on backend development with \textbf{Node.js} \& \textbf{MongoDB}; cooperated with frontend engineers to design state management with React Redux; set up frontend build system with Webpack, Babel \& Gulp}
        \item {Adopted agile development with unit testing \& integration testing using ESLint, Mocha \& Travis CI with \textbf{83\%} of code coverage}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
